Modelling the emergence of whisker barrels

### 2020-06-15 paper/briefpaper/brief.tex
Adds pattern metric section (eta)

% Some document-defined commands
\newcommand*\dif{\mathop{}\!\mathrm{d}}
\newcommand{\cmnt}[1]{\textcolor{blue}{#1}}
\newcommand{\dvrg}{\nabla\vcdot\nabla}
\newcommand{\e}{\emph}
\newcommand{\bol}{\textbf}
\newcommand{\mb}[1]{\mathbf{#1}}
\makeatletter
\newcommand*\vcdot{\mathpalette\vcdot@{.35}}
\newcommand*\vcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
\newcommand{\code}[1]{\textsf{#1}}

@@

\cmnt{Add a description of $\eta$, the pattern-matching measure, here.}

>>>>

% Some document-defined commands
\newcommand*\dif{\mathop{}\!\mathrm{d}}
\newcommand{\cmnt}[1]{\textcolor{blue}{#1}}
\newcommand{\dvrg}{\nabla\vcdot\nabla}
\newcommand{\e}{\emph}
\newcommand{\bol}{\textbf}
\newcommand{\mb}[1]{\mathbf{#1}}
\makeatletter
\newcommand*\vcdot{\mathpalette\vcdot@{.35}}
\newcommand*\vcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
\newcommand{\code}[1]{\textsf{#1}}
% Nice norms:
\usepackage{mathtools}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}

@@

\cmnt{The pattern-matching metric, $\eta$, incorporates information about i)
  the differences in the areas of the simulated and experimental barrels
  ($\mathcal{A}_i^{\mathrm{sim}}$ and $\mathcal{A}_i^{\mathrm{exp}}$); and ii)
  the information provided by `adjacency vectors', $\mathcal{V}_i$ (one for
  each barrel) whose $N$ elements contain the length of the barrel boundary
  which adjoins each other barrel in the pattern. The value of
  $\mathcal{V}_{i,j}$ (the $j^{\mathrm{th}}$ element of $\mathcal{V}_i$) is
  the length of the boundaries between regions of type $i$ and regions of type
  $j$. In a well-formed barrel pattern, $\mathcal{V}_{i}$ is a sparse vector
  and note that $\mathcal{V}_{i,i} = 0, \forall i$. $\mathcal{V}_{i}$ can be
  computed for the experimental and simulated barrel patterns and compared. A
  dimensionless measure of the pattern's arrangement and neighbour relations
  can be obtained from the scalar product of the simulated and experimental
  adjacency vectors:
  $\frac{1}{N} \sum_i \frac { \mathcal{V}_{i}^{\mathrm{sim}}}
  {b_{i}^{\mathrm{sim}} } \vcdot \frac{\mathcal{V}_{i}^{\mathrm{exp}}}{b_{i}^{\mathrm{exp}}}$, where
  $b_i^{\mathrm{exp}}$($b_i^{\mathrm{sim}}$) is the total length of the boundary of
  experimental(simulated) barrel $i$. This measure is low early in the simulation, when the regions do
  not have the neighbour relations of the experimental pattern
  (Fig.\,\ref{fig:main}C, $t=1000$) and maximal when the neighbour relations
  have become established ($t=10000$). It does not distinguish between
  $t=10000$ and $t=30000$.}
%
\cmnt{A second way to analyse the adjacency vectors is to consider
  the mean magnitude of the difference between the simulated and experimental
  vectors: $\frac{1}{N} \sum_i \norm{ \mathcal{V}_{i}^{\mathrm{sim}} -
    \mathcal{V}_{i}^{\mathrm{exp}} } $. This tends to 0 for a perfect
  match and can separate patterns with straight boundaries from those with
  noise on the boundary shape (For an example of `noisy edges', see Fig.\,\ref{fig:sens}B.ii).}
%
\cmnt{We combined all of these measures into a single pattern quality metric:}
%
\begin{equation} \label{eq:eta}
\color{blue}
  \eta =
  \frac
  {
    \frac{1}{N} \sum_i \norm[\big]{ \mathcal{A}_i^{\mathrm{sim}} - \mathcal{A}_i^{\mathrm{exp}} }
    \times
    \frac{1}{N} \sum_i \norm[\big]{ \mathcal{V}_{i}^{\mathrm{sim}} -
      \mathcal{V}_{i}^{\mathrm{exp}} }
  }
  {
    \frac{1}{N}
    \sum_i \frac {\mathcal{V}_{i}^{\mathrm{sim}}} {b_{i}^{\mathrm{sim}}}
    \vcdot
    \frac {\mathcal{V}_{i}^{\mathrm{exp}}} {b_{i}^{\mathrm{exp}}}
  }
\color{black}
\end{equation}
%
\cmnt{which has units of mm$^3$.}
